Enhancing the sales prediction of newly published books by means of computational intelligence methods

### 2016-03-31 paper.tex
Changes and comments

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
***TO DO***: rewrite this considering the new contents and results\\

@@

***TO DO***: complete this considering the new contents and results\\

@@

***TO DO***: rewrite this considering the new structure of the paper\\

@@

***TO DO***: comment the results

***TO DO***: Think if including the graphs (scatter plots).

@@

***TO DO ***: better describe (number of instances) and justify the special cases (why we have chosen them).

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
% ***TO DO***: rewrite this considering the new contents and results\\

@@

%***TO DO***: complete this considering the new contents and results\\

@@

% ***TO DO***: rewrite this considering the new structure of the paper\\

@@

% ***TO DO***: comment the results

% ***TO DO***: Think about including the graphs (scatter plots).

@@

% ***TO DO ***: describe better  (number of instances) and justify the special cases (why we have chosen them).
